---
title: "*Big 5* Analysis with `worldfootballR`"
author: "Alejandro Cepeda"
date: "3/--/2022"
output:
  html_document: default
  pdf_document: default
---

## Project Description

The main purpose of this project is to search for interesting insights from the data provided by the package `worldfootballR`, as well as to hopefully serve as a growing experience in terms of sports analytics and how data science helps improve the world's most popular sport.

The data used will be focused on the teams from **LaLiga Santander**, the Spanish football first division league. The main purpose of this analysis is to provide some sort of insight from expected performances to predict some of the typical football stats, such as xG (expected goals) and xA (expected assists) along with the most up to date data on the performances this season.

```{r setup, message=FALSE}
# libraries
#install.packages("worldfootballR")
#install.packages("tidyverse")
#devtools::install_github("JaseZiv/worldfootballR", ref = "main")
library(worldfootballR)
library(tidyverse)
library(ggrepel)

```

------------------------------------------------------------------------

## Part 1: Data Loading

```{r "Part 1", echo=FALSE}
# loading LaLiga 21/22 FBref data
laLiga.URL <- fb_teams_urls("https://fbref.com/en/comps/12/La-Liga-Stats")
laLiga.teams <- fb_team_player_stats(team_urls=laLiga.URL, stat_type="standard")
head(laLiga.teams)
```

------------------------------------------------------------------------

## Part 2: Non-Penalty xG vs Goals

```{r "Part 2", warning=FALSE}
# plot goal vs xg performance
laLiga.teams %>%
  ggplot(aes(xG_Per_Minutes, Gls_Per_Minutes)) +
  geom_point(size=2) 
```

------------------------------------------------------------------------

## Part 3: Best Passing Teams

```{r "Part 3"}

```
